Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-10 emsoft-2019/related.tex

\citet{Anta10} take an existing controller and its implementation, derive safe
bounds from the controller under which stability is guarantees and verify that
the implementation in fixed-point arithmetic satisfies this error bound.
Similarly, \citet{ParkPSL17} takes an existing floating-point controller
implementation, reconstructs the controller and verifies that roundoff errors
due to finite precision remain below a user-given error bound.

@@

\citet{Abate2017} design safe feedback controllers with counterexample guided
inductive synthesis (CEGIS). Safety verification needs to consider quantization
errors in the controller and in the plant model as the algorithm is based on
bounded model checking (BMC) and tracks roundoff errors with interval
arithmetic. While this algorithm generates the controller and its
implementation, due to limitations in BMC it only considers uniform fixed-point
word length in steps of 8.
\eva{I guess it also does not consider robustness? Not sure how this is related.}

@@

% control-only
\paragraph{Controller Synthesis}
The problem of controller synthesis under safety requirements on the states has
been investigated mostly for Model Predictive Control (MPC)~\cite{camacho2013model} (also called receding horizon control).
Researchers have investigated designing MPC controllers for satisfying safety requirements expressed as temporal logic formulas 
\cite{FMPS18,KaramanSF08,raman2014model,WongpiromsarnTM12,pant2017smooth,kim2017dynamic}.
%,LiNSXL17, SadighK16,
\Sadegh{We can reduce the references.}
The main technique is to optimize the robust satisfaction of 
the formula~\cite{donze2010robust} (i.e., a quantitative measure of satisfaction).
These works utilize MPC an an online method that requires solving at runtime often computationally 
expensive optimization problems. In contrast, the explicit MPC used in our work performs controller synthesis at the design time.

\Sadegh{adding a few references on explicit MPC.}

>>>>

\citet{Anta10} take an existing controller and its implementation, derive safe
bounds from the controller under which stability is guaranteed and verify that
the implementation in fixed-point arithmetic satisfies this error bound.
Similarly, \citet{ParkPSL17} takes an existing floating-point controller
implementation, reconstructs the controller and verifies that roundoff errors
due to finite precision remain below a user-given error bound.

@@

\citet{Abate2017} design safe feedback controllers with counterexample guided
inductive synthesis (CEGIS). Safety verification needs to consider quantization
errors in the controller and in the plant model as the algorithm is based on
bounded model checking (BMC) and tracks roundoff errors with interval
arithmetic. While this algorithm generates the controller and its
implementation, due to limitations in BMC it only considers uniform fixed-point
word length in steps of 8.
\eva{I guess it also does not consider robustness? Not sure how this is related.}
\Sadegh{Eva, You explanation is good. I think the way we look at the problem is different from \cite{Abate2017}: \cite{Abate2017} assumes a fixed precision is given and tries to design the controller with the specific precision such that the safety constraints are satisfied, so no discussion on robustness or memory usage. In our case we don't fix a precision. We find a controller together with a mixed precision that satisfies the constraints and respects the memory budget.}

@@

% control-only
\paragraph{Controller Synthesis}
The problem of controller synthesis under safety requirements on the states has
been investigated mostly for Model Predictive Control (MPC)~\cite{camacho2013model} (also called receding horizon control).
Researchers have investigated designing MPC controllers for satisfying safety requirements expressed as temporal logic formulas 
\cite{FMPS18,KaramanSF08,raman2014model,WongpiromsarnTM12,pant2017smooth,kim2017dynamic}.
%,LiNSXL17, SadighK16,
%\Sadegh{We can reduce the references.}
The main technique is to optimize the robust satisfaction of 
the formula~\cite{donze2010robust} (i.e., a quantitative measure of satisfaction).
These works utilize MPC an an online method that requires solving at runtime often computationally 
expensive optimization problems. In contrast, the explicit MPC used in our work performs controller synthesis at the design time.

%\Sadegh{adding a few references on explicit MPC.}
